Automated troubleshooting toolset for SDNs

### 2013-11-04 draft.tex
conclusion v1

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,draft}

>>>>

This paper has been dedicated to troubleshooting tools in Software-Defined-Network. The methodology used to present them is inspired from the layered architecture of the SDN stack, where each tool has a role to play in at least one layer. From the definition of the different layers, we have introduced tools which aims to find the incoherence between two \textit{state layer}. We introduced a Network Debugger (NDB) designed to find incoherences between policies and their effects. VeriFlow aims at verify invariant between the policy and the Device State. VeryFlow does some model checking technics between the SDN controller and the switches.\\
We also have introduced tools used to find the bug when the incoherence between two \textit{state layer} is identified. These tools operate inside the \textit{code layer} which is for recall, the implementation logic to maintain the mapping between two \textit{state layer}. These tools introduced are SOFT and NICE. SOFT acts on the Physical View and identify incoherence in the OpenFlow implementation between switches of different constructors. NICE can acts either on the controller software or in the switch firmware, it depends where the inconsistency is found by an other tools. \\
The main idea of this paper was to bring an overview of troobleshooting tools in SDNs and how they can works together. As we have explained, thanks to SDN stack, the job can be easely splitted and several tools can be used together to spot bugs.
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,draft}
